---
title: 'Assignment #2 - Processing Data'
author: 'Student_Name'
date: "4/12/2021"
output: html_document
---

```{r echo=TRUE, message=FALSE, warning=FALSE}
options(width = 60)
library(reticulate) ### (... helps Rstudio connect to your python enviroment.)
py_config() # locate the direct path to your 
```

**Instructions** Provide your responses to the following questions in both R and Python. 
Follow the guidelines @  [assign2_guidelines](https://github.com/jkorn81/cu-hsp-learning/tree/main/assignments/assignment2) for more direction.
Also, make sure to use the supporting scripts @ [05_processing_data](https://github.com/jkorn81/cu-hsp-learning/tree/main/05_processing_data).

# Part 1 - Structured Data

**Question #1:** Import the iris csv from the course collection contained in `data` and print the structure of the dataframe using the `str()` function to show a representation of the object.

```{r echo=TRUE}

```

**Question #2:** Subset any of the variables containing `Sepal` from the data. 

```{r echo=TRUE}

```

**Question #3:** Impute Missing/NA Values in the subsetted dataframe. 

```{r echo=TRUE}

```
*Question #4:** Convert the Variables in the dataframe as followed:

- `petal.width` and `petal.length` to numerical type. 
- `variety` to fatcor type. 

```{r echo=TRUE}

```

**Question #5:** Normalize the Data, *(aka. Feature Engineering)* using `center, scale, and corr`.

```{r echo=TRUE}

```
**Bonus Question:** 

Does the last object have the variables in the correct data type? *(yes or no)*

# Part 2 - Unsturctured Text Data 

**Question #6:** Import the `text.csv` file from the course data collection. 

```{r echo=TRUE}

```

**Question #7:** Process the text data and class as reflected in the code contained in file `preprocess_text.r` from lines $10 - 23$. 

```{r echo=TRUE}

```

# Part 3 - Unstructured Image Data

**Question #8:** Locate some images representing two states from the internet *(i.e. sunny skies, cloudy skies)* and sort them into `train and validation` folder scheme and import them as shown in the script `image_processing.r`. Make sure to print back your the number of samples in each folder that you imported.  

```{r echo=TRUE}

```



