---
title: 'Assignment #1 - Exploring the Data'
author: 'Answer Key'
date: "4/12/2021"
output: html_document
---

```{r message=FALSE, warning=FALSE, include=FALSE}
options(width = 60)
library(reticulate) ### (... helps Rstudio connect to your python enviroment.)
py_config() # locate the direct path to your 

```

**Instructions** Provide your responses to the following questions in both R and Python. 
Follow the guidelines @  [assign3_guidelines](https://github.com/jkorn81/cu-hsp-learning/tree/main/assignments/assignment3) for more direction.
Also, make sure to use the supporting scripts @ [06_explore_data](https://github.com/jkorn81/cu-hsp-learning/tree/main/06_explore_data).

# Visualizations 

**Question #1:** Create a boxplot.

```{r}
library(datasets)
data(iris)
data = iris 
library(caret)
featurePlot(x = data[, 1:4], 
            y = data$Species, 
            plot = "box", 
            ## Pass in options to bwplot() 
            scales = list(y = list(relation="free"),
                          x = list(rot = 90)),  
            layout = c(4,1 ), 
            auto.key = list(columns = 2))
```

**Question #2:** Create a barplot.

```{r}
library(ggplot2)
library(datasets)
data(iris)
data = iris 
p = ggplot(data, aes(Species, Sepal.Length)) +
  stat_summary(fun.y = mean,
               geom = "bar",
               fill = "White", 
               color = "Black") + 
  stat_summary(fun.data = mean_cl_normal, 
               geom = "errorbar", 
               position = position_dodge(width = 0.90), 
               width = 0.2) + 
  xlab('X Variable')+
  ylab('Y Variable')
p
```

**Question #3:** Create a density plot.

```{r}
library(datasets)
data(iris)
data = iris 
library(caret)
library(AppliedPredictiveModeling)
transparentTheme(trans = .9)
featurePlot(x = data[, 1:4], 
            y = data$Species,
            plot = "density", 
            ## Pass in options to xyplot() to 
            ## make it prettier
            scales = list(x = list(relation="free"), 
                          y = list(relation="free")), 
            adjust = 1.5, 
            pch = "|", 
            layout = c(4, 1), 
            auto.key = list(columns = 3))
```

**Question #4:** Create a lineplot. 

```{r}
library(ggplot2)
library(datasets)
data(iris)
data = iris 
p = ggplot(data, aes(Species, Sepal.Length)) +
  stat_summary(fun.y = mean, ##adds the points
               geom = "point") +
  stat_summary(fun.y = mean, ##adds the line
               geom = "line",
               aes(group=1)) +
  stat_summary(fun.data = mean_cl_normal, ##adds the error bars
               geom = "errorbar", 
               width = .2) +
  xlab('X Variable')+
  ylab('Y Variable')
p
```

**Question #5:** create a historgram.

```{r}
library(ggplot2)
library(datasets)
data(iris)
data = iris 
p = ggplot(data, aes(Sepal.Width)) + 
    geom_histogram(binwidth = 0.4, color = 'green') + 
    xlab("X Variable") + 
    ylab("Frequency")
p
```

**Question #6:** Create a scatterplot.

```{r}
library(ggplot2)
library(datasets)
data(iris)
data = iris 
p = ggplot(data, aes(Sepal.Width, Sepal.Length)) + 
  geom_point() +
  geom_smooth(method = 'lm', color = 'black') +
  xlab('X Variable')+
  ylab('Y Variable')
p

```

**Question #7:** Create a scatterplot matrix. 

```{r}
library(GGally)
library(datasets)
data(iris)
data = iris 
ggpairs(data, title = 'Sample Iris Data')
```

# Correlation 

**Question #8:** Create a Correlation Matrix.  

```{r}
library(datasets)
data(iris)
data = iris 
cor = cor(data[,c(1:4)])
```

**Question #9:** Create a Correlation Matrix plot.

```{r}
library(datasets)
data(iris)
data = iris 
cor = cor(data[,c(1:4)]) # inputs must be in numeric data type...
#install.packages('corrplot')
corrplot::corrplot(cor)
```

# Statistical Summaries 

**Question #10:** Create at least one statistical summary table as discussed in the course. 

```{r}
library(datasets)
data(iris)
data = iris 
summary(data) #summary function in R
# install.packages('pastecs')
library(pastecs)
stat.desc(quakes[,])
# install.packages('Hmisc')
library(Hmisc)
Hmisc::describe(quakes)
# install.packages('psych')
library(psych)
psych::describe(quakes[,])
```
