---
title: 'Assignment #3 - Exploring the Data'
author: 'Student_Name'
date: "4/12/2021"
output: html_document
---

```{r message=FALSE, warning=FALSE, include=FALSE}
options(width = 60)
library(reticulate) ### (... helps Rstudio connect to your python enviroment.)
py_config() # locate the direct path to your 

```

**Instructions** Provide your responses to the following questions in both R and Python. 
Follow the guidelines @  [assign3_guidelines](https://github.com/jkorn81/cu-hsp-learning/tree/main/assignments/assignment3) for more direction.
Also, make sure to use the supporting scripts @ [06_explore_data](https://github.com/jkorn81/cu-hsp-learning/tree/main/06_explore_data).

# Visualizations 

**Question #1:** Create a boxplot.

```{r}

```

**Question #2:** Create a barplot.

```{r}

```

**Question #3:** Create a density plot.

```{r}

```

**Question #4:** Create a lineplot. 

```{r}

```

**Question #5:** create a historgram.

```{r}

```

**Question #6:** Create a scatterplot.

```{r}

```

**Question #7:** Create a scatterplot matrix. 

```{r}

```

# Correlation 

**Question #8:** Create a Correlation Matrix.  

```{r}

```

**Question #9:** Create a Correlation Matrix plot.

```{r}

```

# Statistical Summaries 

**Question #10:** Create at least one statistical summary table as discussed in the course. 

```{r}

```
