---
title: 'Assignment #4 - Structured and Unstructured Modeling'
author: 'Student_Name'
date: "4/12/2021"
output: html_document
---

```{r message=FALSE, warning=FALSE, include=FALSE}
options(width = 60)
library(reticulate) ### (... helps Rstudio connect to your python enviroment.)
py_config() # locate the direct path to your 

```

**Instructions** Provide your responses to the following questions in both R and Python. 
Follow the guidelines @  [assign4_guidelines](https://github.com/jkorn81/cu-hsp-learning/tree/main/assignments/assignment) for more direction.
Also, make sure to use the supporting scripts @ [07_classical_ml](https://github.com/jkorn81/cu-hsp-learning/tree/main/07_classical_ml) and [08_deep_learning](https://github.com/jkorn81/cu-hsp-learning/tree/main/08_deep_learning).

**Question #1:** Load the `iris.csv` dataset from the course collection and build a classification model as shown in script `decision_tree.r` located in [07_classical_ml](https://github.com/jkorn81/cu-hsp-learning/tree/main/07_classical_ml). Set the target variable as `variety`.

```{r}

```

**Question #2:** Load the `google_estimate_v2.csv` dataset from the course collection and build a regression model as shown in script `regression.r` located in [07_classical_ml](https://github.com/jkorn81/cu-hsp-learning/tree/main/07_classical_ml). Set the target variable as `ACT_CLOSE_PRICE`. 

```{r}

```

**Question #3:** Load the `text.csv` dataset and build/train a supervised deep learning text classifier as shown in script `dl_super_text_classification.r` located in [07_classical_ml](https://github.com/jkorn81/cu-hsp-learning/tree/main/07_classical_ml). *Remember that you may have to pre-process the text data before modeling as discussed in class and shown in script `process_text.r` [05_processing_data](https://github.com/jkorn81/cu-hsp-learning/tree/main/05_processing_data/natural_language_processing).*

```{r}

```

