---
title: "R and Python Learning"
author: "Enter Your Name"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate) #Note this is needed to connect python with Rstudio
```

# Variables:

1.	Create a variable called x whose value corresponds to a number. Print out the value.

```{r q1r}
x = 432
x
```

```{python q1p}
x = 432
print(x)
```

2.	Reassign the value of x to x * 2. Print out the new value of x to verify that it has changed.

```{r q2r}
x = x * 2
x
```

```{python q2p}
x = x * 2
print(x)
```

3.	Try making a character (string) variable. You can call these variables whatever you would like. 

```{r q3r}
charvar = c("a", "string", "variable")
```

```{python q3p}
charvar = ["a", "string", "variable"]
```

# Lists:

4.	Create a numeric vector with three elements using c().

```{r q4r}
numvar = c(1, 2, 3, 4)
```

```{python q4p}
numvar = [1, 2, 3, 4]
```

5.	Create a character vector with three elements using c().

```{r q5r}
charvar2 = c("things", "and", "stuff")
```

```{python q5p}
charvar2 = ["things", "and", "stuff"]
```

6.	Create a numeric vector called age whose elements contain the ages of three people. 

```{r q6r}
age = c(24,32,29)
```

```{python q6p}
age = [24,32,29]
```

7.	Use "indexing by number" to get R and Python to print out the first element of one of the lists you created in the last questions.

```{r q7r}
age[1]
```

```{python q7p}
age[1]
```

# Dataframes:

8.	Load the data contained in the data folder. 
9. Use the $ method to print out the Wind variable in airquality.

```{r q8-9r}
library(readr)
R_Python_learning <- read_csv("data/R&Python_learning.csv")
R_Python_learning$Wind
R_Python_learning$Wind[3]
```

```{python q8-9p}
import pandas as pd
R_Python_learning(r'./data/text.csv')
R_Python_learning[,'Wind']
```

# Functions: 

11.	Make a simple function to calculate x + 6.

```{r q11r}
x = 3
df <- function(x) { 
  print(x + 6)
}
df(x)
```

```{python q11p}
def df(x): 
  return x + 6
x = 3
df(x)
```
