---
title: 'Assignment #1 - R and Python Learning'
author: 'Answer Key'
date: "4/12/2021"
output: html_document
---

```{r message=FALSE, warning=FALSE, include=FALSE}
options(width = 60)
library(reticulate) ### (... helps Rstudio connect to your python enviroment.)
py_config() # locate the direct path to your 

```

**Instructions** Provide your responses to the following questions in both R and Python. 
Follow the guidelines @  [assign1_guidelines](https://github.com/jkorn81/cu-hsp-learning/tree/main/assignments/assignment1) for more direction.
Also, make sure to use the supporting scripts `py_learning.py` and `r_learning.r` @ [04_prepare.tools](https://github.com/jkorn81/cu-hsp-learning/tree/main/04_prepare.tools).


**Question #1:** Store the value 3 as `y` and the value 7 as `x`. 
Provide your response in R in the code chunk below. 

```{r}

```

**Question #2:** Are you able to store and print the same variables in python?

```{python}

```

**Question #3:** Store the x and y variables in a list and print it in R. 

```{r}

```

**Question #4:** Store the x and y variables in a list and print it in Python. 

```{python}

```

**Question #5:** Index the $2^{nd}$ value in the list you stored in your R environment.

```{r}

```

**Question #6:** Index the $2^{nd}$ value in the list you stored in your Python environment.

```{python}

```

**Question #7:** Create a square matrix containing the values $1,2,3,4$ in R. 

```{r}

```

**Question #8:** Create a square matrix containing the values $1,2,3,4$ in Python. 

```{python}

```

**Question #9:** Create a dataframe in R with the column names of `x` and `y` containing $(1,2,3)$ and $(4,5,6)$.

```{r}

```

**Question #10:** Create a function in Python to add $x+y$ and demonstrate it works by adding $3$ and $2$.

```{python}

```

**Question #11:** Create a loop that prints your name at least 10 times in R. 

```{r}

```

**Question #12:** Import the dataset [hiccups.csv](https://github.com/jkorn81/cu-hsp-learning/blob/main/data/Hiccups.csv) in R and print a structure of the data. 

```{r}

```

